Literature Review of Online Question Forums

### 2017-09-25 literature reviews/roughdraft.tex
revised materials/methods section

    The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017. 63.8\% of the questions recieved an answer before the data was downloaded. The distribution of answer times is highly right skewed, shown in figure a. The mean answer time was 355.93 hours, or 14.83 days, and the median answer time is 8.79 hours. These values factor in questions that did not recieve an answer. Within an hour, 26.59\% of the questions received an answer. After one day, 57.35\% of questions recieved an answer. Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.

>>>>

    The data set analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017. We worked exclusively with questions in English. Of the questions in the data set, 4,951, or 63.8\%, recieved an answer before the data was downloaded. Questions that remained unanswered were considered left censored. The time until event value used in survival analysis methods was defined as the time until a question recieves an answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the chosen solution from the asker to be considered the answer. We are only considering the time until the question recieves its first answer. This time until answer variable was calculated as the time from the date it was posted to the date it recieved its first answer, in hours. For left-censored questions, questions that remained unanswered, this value was calculated as the time from the date it was posted to the date the data was downloaded, in hours. Figure a shows the distribution of the answer times for all questions in the data set.

    The following statistics were calculated from Kaplan Meier estimates of the survival probabilities. In our case, survival probability is defined as the probability that a question remains unanswered after a certain time t. The mean survival time, or the average time for questions in the data set to recieve an answer, is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions recieved an answer is 9.16 hours. By 0.88 hours, 52.8 minutes, 25\% of the questions received an answer. By 683.19 hrs, 28.47 days, 64\% of the questions have been answered. Beyond that time point,

    Variables within the data set included information about the questions, like the title, the body text, device, date it was posted, and information about the user like whether or not the user was considered new (or a member for less than 24 hours) at the time the question was posted.
